Information Disclosure Concerns\\in The Age of Wearable Computing

### 2016-02-02 USEC2016-camera-ready/camera-ready.tex
Fixed

\documentclass[conference]{IEEEtran}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\pagestyle{plain}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Information Disclosure Concerns in The Age of Wearable Computing}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Linda Lee, JoongHwa Lee, Serge Egelman, David Wagner}
\IEEEauthorblockA{University of California, Berkeley\\
\{lnl@,dlwndghk94,egelman,daw\}@cs.berkeley.edu}}
%\and
%\IEEEauthorblockN{JoongHwa Lee}
%\IEEEauthorblockA{University of California, Berkeley\\
%dlwndghk94@berkeley.edu }
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%someemail@somedomain.com}}

@@

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test (beyond using mixed effects modeling), given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were not as significant. Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & \textless0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & \textless0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & \textless0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & \textless0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & \textless0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & \textless0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Chi-square tests to examine VUR based on data recipient.}
\label{recipient-chi}
\end{center}
\end{table}

\noindent {\bfseries Open-Ended Concerns}
We asked participants the following open-ended question:

\begin{quotation}
\noindent
\textit{What do you think are the most likely risks associated with wearable devices?}\\
\end{quotation}

@@

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information
\end{enumerate}

@@

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} the loss of money or property
\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing)
\item {\bf Medical:} the disclosure of medical information
\item {\bf Physical:} physical harm to the user
\item {\bf Relationships:} damage to inter-personal relationships
\end{enumerate}

@@

\bibliographystyle{IEEEtran}
\bibliography{bibliography.bib}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
%\usepackage{enumitem}
\usepackage{pdfpages}
\pagestyle{plain}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Information Disclosure Concerns\\in The Age of Wearable Computing}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Linda Lee, JoongHwa Lee, Serge Egelman, David Wagner}
\IEEEauthorblockA{University of California, Berkeley\\
\{lnl,dlwndghk94,egelman,daw\}@cs.berkeley.edu}}
%\and
%\IEEEauthorblockN{JoongHwa Lee}
%\IEEEauthorblockA{University of California, Berkeley\\
%dlwndghk94@berkeley.edu }
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%someemail@somedomain.com}}

@@

This chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test (beyond using mixed effects modeling), given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality. Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were negligible.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & \textless0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & \textless0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & \textless0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & \textless0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & \textless0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & \textless0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Chi-square tests to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}

\noindent {\bfseries Open-Ended Concerns}
To examine privacy and security concerns that may have otherwise not been captured by our scenarios, we asked participants an open-ended question:

\begin{quotation}
\noindent
\textit{What do you think are the most likely risks associated with wearable devices?}
\end{quotation}

@@

\begin{enumerate}%[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information
\end{enumerate}

@@

\begin{enumerate}%[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} the loss of money or property
\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing)
\item {\bf Medical:} the disclosure of medical information
\item {\bf Physical:} physical harm to the user
\item {\bf Relationships:} damage to inter-personal relationships
\end{enumerate}

@@

\section*{Acknowledgements}

We would like to thank the National Science Foundation (NSF) for supporting the first author through a Graduate Research Fellowship. This work was also made possible by the Intel Science and Technology Center for Secure Computing and NSF awards CNS-1514211 and CNS-1514457.

\bibliographystyle{IEEEtranS}
\bibliography{bibliography.bib}
